Extended Formal Analysis of the EDHOC Protocol in Tamarin

### 2022-07-22 formalization.tex
[fix] section 4.3

%---------------------------------------------------------------------- subsub
\subsubsection{System and Adversary Model Extensions Supporting TEE.}
\label{sec:TEE:advModel}
%
We extend the adversary model of~\cite{Norr21} by introducing an interface to
allow the adversary to use the long term key material of any party, though
without directly accessing such key material.
%
This allows us to model the scenario where the adversary has gained access to
a device, but the long term key material is protected by a trusted execution
environment (TEE), and thus only accessible through the TEE interface.
%
According to the terminology of~\cite{DBLP:conf/csfw/Cohn-GordonCG16}, a
protocol is considered to have \emph{weak post-compromise security}
(Weak-PCS) if it achieves its security goals for a specific session
even when the attacker has limited access to the long-term key material
of the parties involved before the session starts -- through an interface 
that maintains the key material secure but allows to run cryptographic 
operations with it -- and full access to the key material of the parties
involved after the end of the session, as well as access to the key material
of all other parties.
%
Seen in the framework of~\cite{DBLP:conf/icics/XuZRWTZ20}, we add adversary
capabilities corresponding to a server adversary, i.e., an adversary that
compromises a party, learns its ephemeral keys and may temporarily access its
TEE, but does not learn the party's long-term key.
%
Our extension to the model of~\cite{Norr21} thus allows us to verify all the
previous security properties under a Weak-PCS model.
%

@@

With this additional attacker capability Tamarin manages to prove
almost all lemmas and method combinations, except for the implicit
authentication lemmas when the responder uses the \mStat{} authentication
method: in these two cases Tamarin did not complete the within reasonable time.
%
We therefore simplified the modeling of XOR encryption of the second
message to prove implicit authentication when the responder uses the 
\mStat{} method.
%
More precisely, the second message encrypts two values: the responder's identity
\verb|R| and the authentication information \verb|authR|.
%
We model XOR encryption by xor-ing each term with their own key-stream term.
%
However for the problematic cases we xor the entire tuple
\verb|<R, authR>| with a single key-stream term.
%
This simplification might miss an attack on implicit authentication that is due
to the combination of a malleable XOR encryption and access to the TEE interface.
%
However, given that no attacks were identified using our original modeling due
to the use of XOR, nor in the current modeling for all other authentication 
methods, we believe that this is not a severe restriction.
%

@@

Users can extend the default term algebra and equational theory in
\mTamarin{} with new function symbols and unification rules for these new 
symbols.
%
For example, \mEdhoc{} requires authenticated encryption, which we model 
using
the symbol \mT{aeadEncrypt}.
%
We augment \mTamarin{} with the following rule for this operation,
which represents the fact that if the adversary knows a key \mT{k},
a message \mT{m}, and authenticated data \mT{ad},
and has access to an encryption algorithm \mT{ai},
then they can obtain the message corresponding to the authenticated 
encryption
of \mT{m} with \mT{k}~\cite{Norr21}.
%
{\footnotesize
\begin{verbatim}
[!KU(k), !KU(m), !KU(ad), !KU(ai)] --[]-> [!KU(aeadEncrypt(k, m, ad, ai))]
\end{verbatim}}
%
We use \mTamarin{}'s builtin rules for other operations, like 
\mXor{}.
%

The rules modeling a Dolev-Yao adversary and the evolution of their 
knowledge
as the protocol executes are built into \mTamarin.
%
We can extend and/or modify this behavior by adding other rules as well.
%
To denote that the adversary has access to a message $p$ at time $t$, we use 
$\mK^{t}(p)$.
%
This 
%stands for the fact that as the adversary interacts with the parties
executing the protocol, at time point $t$, the adversary can derive the
term $p$ using the Dolev-Yao deduction rules and any additional adversary
capabilities specified in \mTamarin.
%
As an example, consider the following implication
\[
    \forall t, k, k'\mLogicDot \mK^{t}(\langle k, k'\rangle)\ \rightarrow\
\mK^{t}(k) \land \mK^{t}(k'),
\]
which represents the fact that if the adversary gets to know the pair of
keys $\langle k, k' \rangle$ at a time point $t$, then the adversary also
knows each of those keys $k$ and $k'$ at time point $t$ as well.
%
For more details about how \mTamarin{} manages adversary knowledge,
see~\cite{DBLP:conf/cav/MeierSCB13}.
%

%-------------------------------------------------------------------------- sub
\subsection{Model and Desired Properties}
\label{sec:desired-properties}
In this section, we describe how we model \mEdhoc{} and the various 
properties
we want it to satisfy.
%

@@

In this work, we consider the following properties:
perfect forward secrecy, injective agreement for both the initiator and the
responder, and implicit agreement.
%
Agreement is considered on a set of parameters $S$ which also contains the
session key material \mSessKey{}.
%
We will first describe in detail both properties, and then describe the
contents of the set $S$.
%
We formalize these properties as shown in Figure~\ref{fig:props}, which is
a modified version of a figure in~\cite{Norr21}.
\begin{figure*}[ht]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, \mRComplete^{t_2}(\mTID, I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \lor t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \lor t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \lor t_1 \lessdot t_2))\\[2em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot \mRComplete^{t_1'}(\mTID_R', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID_R, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \lor t_1 \lessdot t_2))\\[2em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot \mIComplete^{t_1}(\mTID_I, I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \lor t_1 \lessdot t_2))
\end{align*}
%
\caption{Formalization of security properties and adversary model.}
\label{fig:props}
\end{figure*}

%----------------------------------------------------------------------- PFS
\subsubsection{Perfect Forward Secrecy (PFS).}
\label{sec:secrecy}
Informally, by perfect forward secrecy, we mean that the adversary cannot
gain access to the session key material \mSessKey{}, even if a long-term key is
leaked after the establishment of \mSessKey{}.
%
PFS for session key material \mSessKey{} is formalized as \mPredPcs{}
in Figure~\ref{fig:props}.
%

In the \mIComplete{} event, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PFS property states that an adversary obtains \mSessKey{}
only if a party's long-term key is compromised before their run ends, if an
ephemeral key is compromised at any time after a party's run began.
%
This is to hold even if the adversary has access to the TEE of either party
before and after the protocol execution.
%
The property in Figure~\ref{fig:props} is unlike the actual \mTamarin{} lemma
in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(I, R, \mSessKey)\, \lor\,  \mRComplete^{t_2}(I, R, 
\mSessKey)$
to model the fact that either party can have completed their execution, we use
a single action parametrized by the terms $I$, $R$, and \mSessKey.

@@

%
We formalize injective agreement for the initiator role as \mPredInjI{} and
for the responder role as \mPredInjR{} in Figure~\ref{fig:props}.
%
For the initiator $I$, this property represents the fact that either
injective agreement (as described above) holds, or the long-term key of
the party $R$ assumed to be playing the responder role has been
compromised before $I$'s role finished.
%
The property is to hold even if the adversary has access to the TEE of party $R$
before and after the protocol execution.
%
%If the adversary has managed to compromise $R$'s long-term key, they can
%generate any message of their liking and sign it using said key,
%or compute a $\mathit{MAC}_{R}$ using the long-term keys \mPubE{I},
%\mPriv{R}, and an ephemeral key pair $\langle\mPrivE{R},\ 
%\mPubE{R}\rangle$
%of 
%their choice.
%%
The analogous definition holds for the responder $R$.
%

%------------------------------------------------------------- Implicit auth
As part of our analysis, we found that all the \mEdhoc{} methods satisfy PFS.
%
However, this is not the case for the injective agreement property as stated 
above.
%
Thus, we show a different property, a form of implicit agreement on the same
set of parameters, which is guaranteed for all methods.
%
This modification is inspired by the definitions of implicit authentication in
the computational model~\cite{DBLP:conf/csfw/GuilhemFW20}.
%
While that paper focuses on authenticating just a key and related identities,
our definition encompasses a general set of parameters, as in the notion of
injective agreement proposed by Lowe~\cite{DBLP:conf/csfw/Lowe97a}.

>>>>

%---------------------------------------------------------------------- subsub
\subsubsection{System and Adversary Model Extensions Supporting TEE.}
\label{sec:TEE:advModel}
%
We extend the adversary model of~\cite{Norr21} by introducing an interface to
allow the adversary to use the long term key material of any party, though
without directly accessing such key material.
%
This allows us to model the scenario where the adversary has gained access to
a device, but the long term key material is protected by a trusted execution
environment (TEE), and thus only accessible through the TEE interface.
%
According to the terminology of~\cite{DBLP:conf/csfw/Cohn-GordonCG16}, a
protocol is considered to have \emph{weak post-compromise security}
(Weak-PCS) if it achieves its security goals for a specific session
even when the attacker has limited access to the long-term key material
of the parties involved before the session starts -- through an interface 
that maintains the key material secure but allows to run cryptographic 
operations with it -- and full access to the key material of the parties
involved after the end of the session, as well as access to the key material
of all other parties.
%
Seen in the framework of~\cite{DBLP:conf/icics/XuZRWTZ20}, we add adversary
capabilities corresponding to a server adversary, i.e., an adversary that
compromises a party, learns its ephemeral keys and may temporarily access its
TEE, but does not learn the party's long-term key.
%
Our extension to the model of~\cite{Norr21} thus allows us to verify all the
previous security properties under a Weak-PCS model.
%
Note that this attacker model is strictly more powerful than that of~\cite{Norr21},
as it maintains all the previous attacker capabilities.
%

@@

With this additional attacker capability Tamarin manages to prove
almost all lemmas and method combinations, except for the implicit
authentication lemmas when the responder uses the \mStat{} authentication
method: in these two cases Tamarin did not complete the within reasonable
time\footnote{See Table~\ref{tab:props} for all verification results and
computation times.}.
%
We therefore simplified the modeling of XOR encryption of the second
message to prove implicit authentication when the responder uses the 
\mStat{} method.
%
More precisely, the second message encrypts two values: the responder's identity
\verb|R| and the authentication information \verb|authR|.
%
We model XOR encryption by xor-ing each term with their own key-stream term.
%
However for the problematic cases we xor the entire tuple
\verb|<R, authR>| with a single key-stream term.
%
This simplification might miss an attack on implicit authentication that is due
to the combination of a malleable XOR encryption and access to the TEE interface.
%
However, given that no attacks were identified using our original modeling due
to the use of XOR, nor in the current modeling for all other authentication 
methods, we believe that this is not a severe restriction.
%

@@

Users can extend the default term algebra and equational theory in
\mTamarin{} with new function symbols and unification rules for these new 
symbols.
%
For example, \mEdhoc{} requires authenticated encryption, which we model 
using
the symbol \mT{aeadEncrypt}.
%
We augment \mTamarin{} with the following rule for this operation,
which represents the fact that if the adversary knows a key \mT{k},
a message \mT{m}, and authenticated data \mT{ad},
and has access to an encryption algorithm \mT{ai},
then they can obtain the message corresponding to the authenticated 
encryption
of \mT{m} with \mT{k}~\cite{Norr21}.
%
{\footnotesize
\begin{verbatim}
[!KU(k), !KU(m), !KU(ad), !KU(ai)] --[]-> [!KU(aeadEncrypt(k, m, ad, ai))]
\end{verbatim}}
%
Other than modeling authenticated encryption, we use \mTamarin{}'s builtin
equational theories for signing, Diffie-Hellman, hashing and \mXor{}.
%

Tamarin has also built-in rules for modeling a Dolev-Yao adversary and the
evolution of their knowledge as the protocol executes.
%
We extend the Dolev-Yao adversary model by adding other rules that increase
the capabilities of the attacker.
%
To denote that the adversary has access to a message $p$ at time $t$, we use 
$\mK^{t}(p)$.
%
\anote{Removed:
This stands for the fact that as the adversary interacts with the parties
executing the protocol, at time point $t$, the adversary can derive the
term $p$ using the Dolev-Yao deduction rules and any additional adversary
capabilities specified in \mTamarin.}
%
As an example, the following implication
\[
    \forall t, k, k'\mLogicDot \mK^{t}(\langle k, k'\rangle)\ \rightarrow\
\mK^{t}(k) \land \mK^{t}(k'),
\]
models that if the adversary gets to know the pair of
keys $\langle k, k' \rangle$ at a time point $t$, then the adversary also
knows each of those keys $k$ and $k'$ at time point $t$ as well.
%
For more details about how \mTamarin{} manages adversary knowledge,
see~\cite{DBLP:conf/cav/MeierSCB13}.
%

%-------------------------------------------------------------------------- sub
\subsection{Model and Desired Properties}
\label{sec:desired-properties}
In this section we describe our modeling of \mEdhoc{} and its desired
security properties.
%

@@

In this work we consider the following properties: secrecy of the session key,
injective agreement and implicit agreement of the session key material for both
initiator and responder, and secrecy and integrity of the application data sent
on message 3 ($\mAD_3$)
%
Agreement is considered on a set of parameters $S$ which also contains the
session key material \mSessKey{}.
%
We will first describe in detail both properties, and then describe the
contents of the set $S$.
%
We formalize these properties as shown in Figure~\ref{fig:props}, which is
a modified version of a figure in~\cite{Norr21}.
\begin{figure*}[ht]
\begin{align*}
    \mPredPcs \triangleq\ & \forall \mTID, I, R, \mSessKey, t_2, t_3\mLogicDot
    \mK^{t_3}(\mSessKey)\  \land\ 
    (\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, \mRComplete^{t_2}(\mTID, I, R, 
\mSessKey))
    \rightarrow\\
    &(\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)
    \ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(R, \mSessKey))
    \ \lor\ (\exists t_1\mLogicDot \mRevEph^{t_1}(I, \mSessKey))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_2\mLogicDot \mIComplete^{t_2}(I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_R, t_1\mLogicDot \mRStart^{t_1}(\mTID_R, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_I', I', R', t_1' \mLogicDot \mIComplete^{t_1'}(\mTID_I', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(R) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredInjR \triangleq\ &
    \forall \mTID_R, I, R, \mSessKey, S, t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I, R, 
\mSessKey, S)
    \rightarrow\\
    &(\exists \mTID_I, t_1\mLogicDot \mIStart^{t_1}(\mTID_I, I, R, \mSessKey, S) \land t_1 \lessdot t_2
    \land (\forall \mTID_R', I' R' t_1' \mLogicDot \mRComplete^{t_1'}(\mTID_R', I' , R', \mSessKey, S)
        \rightarrow t_1' \doteq t_1))\\
    &\ \lor\ (\exists t_1\mLogicDot \mRevLTK^{t_1}(I) \land t_1 \lessdot t_2)\\
    &\ \lor\ (\exists t_0, t_1\mLogicDot \mRStart^{t_0}(\mTID_R, R, \mSessKey, S) \land \mTEE^{t_1}(I) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))\\[2em]
%
    \mPredImpI \triangleq\ &
    \forall \mTID_I, I, R, \mSessKey, S, t_1\mLogicDot \mIComplete^{t_1}(\mTID_I, I, R, \mSessKey, 
S)
    \rightarrow\\
      &(\forall \mTID_R, I', R', S', t_2\mLogicDot \mRComplete^{t_2}(\mTID_R, I', R', \mSessKey, S') \rightarrow
             (I=I' \land R=R' \land S=S')\\
      &\ \ \land (\forall \mTID_I', I', R', S', t_1'\mLogicDot
        \mIComplete^{t_1'}(\mTID_I', I', R', \mSessKey, S') \rightarrow t_1' \doteq t_1
        ))\\
    &\lor(\exists t_0\mLogicDot \mRevLTK^{t_0}(R) \land t_0 \lessdot t_1)
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(R, \mSessKey))
    \lor(\exists t_0\mLogicDot \mRevEph^{t_0}(I, \mSessKey))\\
    &\lor\ (\exists t_0, t_1\mLogicDot \mIStart^{t_0}(\mTID_I, I, R) \land \mTEE^{t_1}(R) \land (t_0 \lessdot t_1 \land t_1 \lessdot t_2))
\end{align*}
%
\caption{Formalization of security properties and adversary model.}
\label{fig:props}
\end{figure*}

%----------------------------------------------------------------------- PFS
\subsubsection{Secrecy of the session key material.}
\label{sec:secrecy}
We show that the adversary cannot gain access to the session key material \mSessKey{},
even under a weak post-compromise security model that allows the adversary limited access
to the long-term keys of the parties involved through a secure interface before the session starts, 
unrestricted access to the long-term keys of the involved parties after the session ends
and of all other parties, as well as access to all other session keys.
%
This property is formalized as \mPredPcs{}
in Figure~\ref{fig:props}.
%

In the \mIComplete{} event, \mTID{} represents a ``thread identifier'' for the
current session, $I$ represents the identity of the initiator,
and $R$ represents the identity of the party who the initiator believes is
playing the responder role, while \mSessKey{} stands for the established
session key material.
%
\mRComplete{} has analogous parameters; in particular, the responder $R$
believes $I$ is the party playing the initiator role.
%
Intuitively, the PCS property states that an adversary obtains \mSessKey{}
only if one of the following conditions hold: either a party's long-term key
is compromised before their run ends, or \mSessKey{} is directly revealed to
the attacker, or the TEE interface for the responder is used during the current
session for the initiator (i.e. after the initiator starts and before it
commits), or, similarly, the TEE interface for the initiator is used during the
current session for the responder.
%
The property in Figure~\ref{fig:props} is unlike the actual \mTamarin{} lemma
in one minor way: \mTamarin's logic does not allow disjunctions to appear on
the left-hand side of an implication inside a universally-quantified formula.
%
Therefore, in the \mTamarin{} code, instead of using the disjunction
$\mIComplete^{t_2}(\mTID, I, R, \mSessKey)\, \lor\, 
\mRComplete^{t_2}(\mTID, I, R, \mSessKey)$
to model the fact that either party may have completed their execution, we use
a single action parametrized by the terms $\mTID$, $I$, $R$, and \mSessKey.

@@

%
We formalize injective agreement for the initiator role as \mPredInjI{} and
for the responder role as \mPredInjR{} in Figure~\ref{fig:props}.
%
For the initiator $I$, this property represents the fact that either
injective agreement (as described above) holds, or the long-term key of
the party $R$ assumed to be playing the responder role has been
compromised before $I$'s role finished.
%
The property should hold even if the adversary has access to the TEE of party $R$
before and after the protocol execution.
%
%If the adversary has managed to compromise $R$'s long-term key, they can
%generate any message of their liking and sign it using said key,
%or compute a $\mathit{MAC}_{R}$ using the long-term keys \mPubE{I},
%\mPriv{R}, and an ephemeral key pair $\langle\mPrivE{R},\ 
%\mPubE{R}\rangle$
%of 
%their choice.
%%
An analogous definition holds for the responder $R$.
%

%------------------------------------------------------------- Implicit auth
As part of our analysis, we found that all the \mEdhoc{} methods satisfy weak
pot-compromise security.
%
However, this is not the case for the injective agreement property as stated 
above.
%
Thus, we show a different property, a form of implicit agreement on the same
set of parameters, which is guaranteed for all methods.
%
This modification is inspired by the definitions of implicit authentication in
the computational model~\cite{DBLP:conf/csfw/GuilhemFW20}.
%
While that paper focuses on authenticating just a key and related identities,
our definition encompasses a general set of parameters, as in the notion of
injective agreement proposed by Lowe~\cite{DBLP:conf/csfw/Lowe97a}.
